Analyzing the Impact of Social Attributes on Commit Integration Success

### 2017-03-27 Paper/MSRChallenge2017.tex
edits through end of eval

\usepackage{booktabs}
\usepackage{verbatim}
\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}

@@

\vspace{1ex}
\noindent\textbf{Metric.} We measure software contribution quality by the
build status of the
commit. We used a decision tree classifier~\cite{Quinlan86} to identify
important factors in predicting build success;  decision trees are well
established and interpretable. We use a J48 decision tree, which
has the ability to identify which attributes 
discriminate the various instances most clearly.
We first build a
decision tree classifier using only technical factors to 
predict build integration
success.  We then include the social factors, to 
identify the degree to which the social factors improve the model's predictive
power.
We evaluate the models with 10-fold cross-validation.

@@

\hline
\end{tabular}
\\
\center
	\caption{\label{resultsTable} Predictive power 
      decision trees with a non-downsampled dataset
	(2\textsuperscript{nd} and 3\textsuperscript{rd} column) and downsampled
	(4\textsuperscript{th} and 5\textsuperscript{th} column). 
	%The higher the percentages represent the higher number of instances we are able to correctly predict. \label{resultsTable}
	%Zack: the above sentence isn't true for the second row.
	}   
\end{table*}
To address our main research question: ``Do social attributes, gathered 
from the GitHub profiles of developers,
allow for more accurate predictions than only using technical data?", we 
created a decision tree classifier~\cite{Quinlan86}.
Decision trees are a predictive model which uses binary decisions on the
attributes to predict a final class.  The predicted class is represented as the
leaves, while the attribute decisions used in the prediction cause the
different branches.
In this study, we used the Weka J48 decision tree~\cite{Weka,Quinlan1993}
with default settings. The decision trees were evaluated using 10-fold 
cross-validation with the data in each data set.

In Section~\ref{sec:successClassification} we discuss the build classification
success rate for the technical and social factors.  In Section~\ref{sec:core},
we compare the build success rate of core project members to non-core project
members.  In Section~\ref{sec:followerSuccess}, we compare the relationship
between a developer's followers and the build integration success.

@@

It is also worth noting that the Kappa statistic increases in both cases when
adding social data (100\% and 85\% respectively). The Kappa statistic is a measurement that also accounts for the accuracy of the predicting power of the model. Furthermore, Kappa is a more 
robust measure than \textit{correctly classified} instances, since it takes into account the
correctly guessed instances occurring by chance. The mean absolute error also
decreases in both cases, which provides further evidences that social factors
are important when predicting build success.

@@

Based on the decision tree results, we noticed that core team members were
important when classifying build success, so we decided to investigate if core
team members have greater build success rates.
We classified the build success rate for
core team members and non-core team members using the data set without 
downsampling.  We found that core team members
triggered 89.39\% (331827/371208) of the builds in the data set and 75.58\%
(250808/331827) of those builds
passed.  Non-core team members triggered 10.61\% (39381/371208) of the builds 
in the data set
and 64.70\% (25479/39381) of the builds passed.  This shows that core team 
members are more
likely to have a successful build integration than non-core team members. We hypothesize the reason for this to be that core team members are more familiar with the code, therefore are more likely to have their builds pass.

@@

We also investigated whether developers with followers were more likely to have a
successful build integration, since followers may be seen as vouching for
the developer's abilities.  We specifically investigated if a developer with 
followers was more likely to pass the build in the data set without 
downsampling.  We first investigated whether developers with one or more followers
were more likely to pass the build than developers without any followers, to
verify the assumption that followers vouch for a developer's abilities. To
investigate this question, we removed the commits without author profile
information (20374 builds which reduced the total build count from 371208 to
350834). We found 
that only 0.87\% (3059/350834) of the
contributions in the data set were performed by developers with zero 
followers. We found that 99.13\% (347775/350834) of the contributions 
were performed by
developers with at least one or more followers.
Developers with 0 followers had a successful build commit 68.49\% (2095/3059)
of the time.  Developers with one or more followers were successful 74.78\%
(260056/347775) of the time.

We also investigated developers with a large number of followers (1000 or more
followers).  We found that 6.94\% (24347/350834) of the contributions in the 
data set were
performed by developers with 1000 or more followers.  We found that these
contributions had a 78.61\% (19138/24347) success rate.  These results show 
developers
with more followers are more likely to have a successful integration build.
These
result may be due to the fact that developers with followers are more likely to
have open source development experience, and the developers' experience
influenced the build success rate..

\subsection{Discussion}

Overall, we have found that social attributes which proxy experience, such as if
the developer is a core project contributor , produce a 
noticeable increase in predicting build success.  While the increase was noticeable 
with the full data set, there was a much greater increase in prediction
accuracy after performing downsampling. These results show that social factors,
such 
as the ones studied in this paper, are significant predictors when
evaluating the predictive power of build commit success.

The build success by core team member results show that core team members are
more likely to have the build integration pass than non-core team members.  This
result provides evidence that non-core team member commits are not as
scrutinized as core team member commits before the integration build tests, although further studied will be required to draw definite
conclusions.

The follower results indicate that developers with more followers are more
likely to pass the build, although followers are not a perfect indicator.
Developers with over 1000 followers had more than a 10\% increase compared to
developers with no followers.  This shows that higher quality open source developers are more
likely to have a large number of followers.

Overall, we have found that while experience is not a perfect indicator, 
experienced developers are more likely to make high quality project commits.

@@

\bibliographystyle{plain}
\bibliography{MSRChallenge2017}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references

>>>>

\usepackage{booktabs}
\usepackage{verbatim}
\usepackage{balance}
\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}

@@

\vspace{1ex}
\noindent\textbf{Metric.} We measure software contribution quality by the
build status of the
commit. We used a decision tree classifier~\cite{Quinlan86} to identify
important factors in predicting build success. Decision trees are a predictive model which uses binary decisions on the
attributes to predict a final class. They are well
established and interpretable. We use a J48 decision tree, which
has the ability to identify which attributes 
discriminate the various instances most clearly.
We first build a
decision tree classifier using only technical factors to 
predict build integration
success.  We then include the social factors, to 
identify the degree to which the social factors improve the model's predictive
power.
We evaluate the models with 10-fold cross-validation.

@@

\hline
\end{tabular}
\\
\center
	\caption{\label{resultsTable} Predictive power 
      decision trees with a non-downsampled dataset
	(2\textsuperscript{nd} and 3\textsuperscript{rd} column) and downsampled
	(4\textsuperscript{th} and 5\textsuperscript{th} column). 
	%The higher the percentages represent the higher number of instances we are able to correctly predict. \label{resultsTable}
	%Zack: the above sentence isn't true for the second row.
	}   
\end{table*}

We created decision tree classifiers~\cite{Quinlan86} to address our main research question: ``Do social attributes, gathered 
from the GitHub profiles of developers,
allow for more accurate predictions than only using technical data?''
%   The predicted class is represented as the
% leaves, while the attribute decisions used in the prediction cause the
% different branches.
We used the Weka J48 decision tree~\cite{Weka,Quinlan1993}
with default settings. We mitigate the risk of overfitting through 10-fold 
cross-validation.

In Section~\ref{sec:successClassification} we discuss the build classification
success rate for the technical and social factors.  In Section~\ref{sec:core},
we compare the build success rate of core project members to non-core project
members.  In Section~\ref{sec:followerSuccess}, we compare the relationship
between a developer's followers and build integration success.

@@

It is also worth noting that the Kappa statistic increases in both cases when
adding social data (100\% and 85\% respectively). The Kappa statistic is a measurement that also accounts for the accuracy of the predicting power of the model. Furthermore, Kappa is a more 
robust measure than \textit{correctly classified} instances, since it takes into account the
correctly guessed instances occurring by chance. The mean absolute error also
decreases in both cases, providing further evidence that social factors
importantly predict build success.

@@

The decision tree results suggested that core team members are
important to classifying build success, and thus we investigated the question
directly. 
We classified the build success rate for
core team members and non-core team members using the data set without 
downsampling.  We found that core team members
triggered 89.39\% (331827/371208) of the builds in the data set and 75.58\%
(250808/331827) of those builds
passed.  Non-core team members triggered 10.61\% (39381/371208) of the builds 
in the data set
and 64.70\% (25479/39381) of the builds passed.  This shows that core team 
members are more
likely to have a successful build integration than non-core team members. We hypothesize the reason for this to be that core team members are more familiar with the code, therefore are more likely to have their builds pass.

@@

We also investigated whether developers with followers were more likely to have a
successful build integration, since followers may be seen as ``vouching'' for
the developer's abilities.  We therefore investigated the relationship between
follower count and build success rate (on the data without 
downsampling).  We first investigated whether developers with one or more followers
were more likely to pass the build than those without any followers by
removing commits without any author profile
information (20374 builds, reducing the total build count to
350834). Only 0.87\% (3059/350834) of the
contributions in the data set were performed by developers with zero 
followers.  %, leaving 99.13\% (347775/350834) of the contributions 
%performed by developers with at least one follower.
Developers with 0 followers had a successful build commit 68.49\% (2095/3059)
of the time.  Developers with one or more followers were successful 74.78\%
(260056/347775) of the time.
%
By contrast, developers with a large number of followers (1000 or more),
performed 6.94\% (24347/350834) of the contributions in the 
data set; their
contributions had a 78.61\% (19138/24347) success rate.

These results suggest that developers
with more followers are more likely to have a successful integration build.
This may be due to the fact that developers with followers are more likely to
have open source development experience, and the developers' experience
influenced their build success.

\subsection{Summary}

Social attributes proxying experience, such as whether
the developer is a core project contributor,
noticeably influence build success prediction.  While the increase was noticeable 
with the full data set, there was a much greater increase in prediction
accuracy after downsampling. 
%These results suggest that social factors
%are significant predictors when
%evaluating the predictive power of build commit success.
%
In particular, core team members are
more likely to have the build integration pass than non-core team members.  This
result provides evidence that non-core team member commits may not be as
scrutinized as core team member commits before the integration build tests,
although further study is required to draw definitive
conclusions.
%
Likewise, developers with more followers are more
likely to pass the build, although followers are not a perfect indicator.
Developers with 1000+ followers were more than a 10\% more succesful in their
builds as compared to
developers with no followers.  This suggests that open source developers with
high quality commits may be more
likely to have a large number of followers.

Overall, although experience is an imperfect indicator, but
experienced developers appear more likely to make high quality commits.

@@

\balance
\bibliographystyle{plain}
\bibliography{MSRChallenge2017}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
